Understanding domestic abuse

### 2019-07-29 JeS_fields.tex
Update JeS_fields.tex

The primary ethical concerns in this project centre around data privacy and data security. In particular, both the Crime Survey for England and Wales (secure access, low-level geographic data) and  the West Midlands Police datasets are highly sensitive. If data were to end up in the wrong hands could be particularly damaging for the individuals present in the data, as well as for the WMP force, and even the researchers. For this reason we have developed our data security approach in tandem with WMP to ensure that data is only ever held and transported securely, and that researchers hold only the minimum amount of information in order to perform the research. We also meet all of the standards for data security for accessing the secure access version of the Crime Survey for England and Wales.

>>>>

The primary ethical concerns in this project centre around data privacy and data security. In particular, the West Midlands Police datasets are highly sensitive. If data were to end up in the wrong hands could be particularly damaging for the individuals present in the data, as well as for the WMP force, and even the researchers. For this reason we have developed our data security approach in tandem with WMP to ensure that data is only ever held and transported securely, and that researchers hold only the minimum amount of information in order to perform the research.
